---
title: "p8105_hw2_akg2197"
author: "Annie Gorman"
date: "2024-09-29"
output: github_document
---
```{r setup}
library(tidyverse)
```

## Problem 1

## Problem 2

```{r}
library(readxl)
trashwheel_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 1, range = "A2:N653")

trashwheel_df=trashwheel_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

trashwheel_df = trashwheel_df |>
  mutate(sports_balls = as.integer(sports_balls))

library(readxl)
proftrashwheel_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 2, range = "A2:M121")

proftrashwheel_df=proftrashwheel_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

library(readxl)
gwynnda_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 4, range = "A2:L265")

gwynnda_df=gwynnda_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

dplyr:::left_join.data.frame(trashwheel_df, proftrashwheel_df, gwynnda_df, by = "volume_cubic_yards")
```
## Problem 3 
```{r}
bakers = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakers.csv")
bakes = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakes.csv")
results = read_csv("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/results.csv")
```
bakers=
  bakers |> rename(baker = 'Baker Name')
bakes = 
  bakes |> rename(baker = 'Baker')

results = results |>
  rename(series = `...1`, episode = `...2`, baker = `...3`, technical = `...4`, result = `IN = stayed in; OUT = Eliminated; STAR BAKER = Star Baker; WINNER = Series Winner; Runner-Up = Series Runner Up; WD = Withdrew` )

results = results |>
select(series, episode, baker, technical, result)

anti_join(bakes, bakers, by = c("Baker", "Baker Name"))
anti_join(results, bakers, by = c("Baker", "Series))
