---
title: "p8105_hw2_akg2197"
author: "Annie Gorman"
date: "2024-09-29"
output: github_document
---
```{r setup}
library(tidyverse)
```

## Problem 1

## Problem 2

```{r}
library(readxl)
trashwheel_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 1, range = "A2:N653")

trashwheel_df=trashwheel_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

trashwheel_df = trashwheel_df |>
  mutate(sports_balls = as.integer(sports_balls))

library(readxl)
proftrashwheel_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 2, range = "A2:M121")

proftrashwheel_df=proftrashwheel_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

library(readxl)
gwynnda_df <- read_excel("~/Downloads/202409 Trash Wheel Collection Data.xlsx", sheet = 4, range = "A2:L265")

gwynnda_df=gwynnda_df |>
  janitor::clean_names()|>
  drop_na(dumpster)

gwynnda_df =
  gwynnda_df %>% 
  filter(
    month == "June",
    year == "2022"
  )

sum(select(gwynnda_df, cigarette_butts))
```
The merged dataset has  `r nrow(trashwheel_df)` rows and `r ncol(trashwheel_df)` columns. The variables include trash wheel name (trash_wheel), dumpster number (dumpster), weight in tons (weight_tons), and volume in cubic yds (volume_cubic_yards). Total weight of trash collected by Professor Trash Wheel for the available data was `r sum(select(prof_trash_wheel, weight_tons))` tons. Total number of cigarette butts collected by Gwynnda in June 2022 was 18,120.

## Problem 3 
```{r}
<<<<<<< HEAD
bakers = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakers.csv", na =c("", "N/A", "Unknown", "UNKNOWN")) |>
  janitor::clean_names()
bakes = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakes.csv") |>
 janitor::clean_names()
results = read_csv("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/results.csv", skip = 2), c("", "N/A", "Unknown", "UNKNOWN")) |>
 janitor::clean_names()
 
bakers=
  bakers |> rename(baker = baker_name)
bakes = 
  bakes |> rename(baker = baker)

anti_join(bakers, bakes, by = c("series", "baker"))

## merging
bakeoff_df =
  full_join(results, bakes, by = c("series", "episode", "baker"))|> 
  full_join(bakers, by = c("series", "baker")

head(bakeoff_df)

bakeoff_df=
  select(episode, series, baker, result, technical, results) |>

write.csv(bakeoff_df, "bakeoff_clean_set.csv", row.names = FALSE)|>
```

In the cleaning of my data, I have shown the series, bakers and their signature dishes, episode, and "show stoppers." Renaming bakers and bakes was necessary in merging the datasets. The dataset is `r nrow(bakeoff_df)` and `r ncol(bakeoff_df)`.

```{r}
star_baker_df = bakeoff_df |>
  filter(series >=5, results %in% c("STAR BAKER", "WINNER")) |>
  select(series, episode, baker)

head(star_baker_df)

colnames(results)
colnames(bakes)
colnames(bakers)
```
The predictable winner was Jo. Jo was the overall winner with no other surprises in seasons 5-10. 
=======
bakers = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakers.csv")
bakes = read_csv ("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/bakes.csv")
results = read_csv("~/Desktop/p8105_hw2_akg2197/gbb_datasets 2/results.csv")
```
bakers=
  bakers |> rename(baker = 'Baker Name')
bakes = 
  bakes |> rename(baker = 'Baker')

results = results |>
  rename(series = `...1`, episode = `...2`, baker = `...3`, technical = `...4`, result = `IN = stayed in; OUT = Eliminated; STAR BAKER = Star Baker; WINNER = Series Winner; Runner-Up = Series Runner Up; WD = Withdrew` )

results = results |>
select(series, episode, baker, technical, result)

anti_join(bakes, bakers, by = c("Baker", "Baker Name"))
anti_join(results, bakers, by = c("Baker", "Series))
>>>>>>> af3ea8297f5757a0d887b222da09686c50a9c9f3
